---
title: "Cyclistic User Patterns"
author: "Case Study"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

setwd("../Cyclistic_bikes/Code")
source("Cyc_run.R", echo=FALSE)
setwd("..")
```

```{r code_read, include=FALSE, cache=FALSE}
knitr::read_chunk("Code/start_code.R")
```

```{r, test-b, echo=FALSE, eval=TRUE}
# Calculate the number of records missing station names
# Calculate the number of records missing start date/times
```
There are a total of ``r t_gb`` records in the dataset.

``r start_missing`` of the records are missing the start time for the ride.  These records (if any) will not be included in the monthly, daily or hourly traffic analysis.

``r station_missing`` of the records are missing the start station name for the ride.  Any records missing the start time or the station name will not be included in the station traffic analysis.


```{r child_rmd, child="Code/Cap_Stone.Rmd"}
# Calling the analytics report, tables, graphs and such
```

